---
title: "Batch import with get_spec() and get_metadata()"
author: "Hugo Gruson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

`lightr` provides three main functions for patch import of spectral data and
metadata:

* `get_spec()`
* `get_metadata()`
* `spec2csv()`

Those three functions contain a loop and can directly be used to import/convert
whole folders.

They also allow for recursive search in the folder tree with the argument
`subdir`. In this example, the `data` that contains a subdirectory named `procspec_files`, which contains :

```
data
├── avantes_export.ttt
├── avantes_export2.trt
├── avantes_export_long.ttt
└── procspec_files
    ├── OceanOptics_badencode.ProcSpec
    ├── OceanOptics_Linux.ProcSpec
    ├── OceanOptics_Windows.ProcSpec
    └── whiteref.ProcSpec
```

We first demonstrate these features on `get_spec()` but they work in the same
way for `get_metadata()` and `spec2csv()`

```{r}
library(lightr)
```

## `get_spec()`

`get_spec()` is one the core functions of `lightr`. It finds spectral data 
files, extract the reflectance / transmittance / absorbance data and returns a
`data.frame` where the first column (named `wl`) contains the wavelengths and
the subsequent columns contain the spectral data, interpolated every nanometre:

```{r}
res <- get_spec(where = "data", ext = "ttt", lim = c(300, 700))
head(res)
```

`get_spec()` also supports setting multiple file extensions at once by passing
a character vector to `ext`:

```{r}
res <- get_spec(where = "data", ext = c("ttt", "trt"), lim = c(300, 700))
head(res)
```

Finally, `get_spec()` can also recursively search in your folder tree with the
`subdir` argument:

```{r}
res <- get_spec(where = "data", ext = "procspec", lim = c(300, 700), subdir = TRUE)
head(res)
```

As you may have noticed, `get_spec()` does not care about the file extension
case by default. This can be changed by using the `ignore.case` switch:

```{r}
res <- get_spec(where = "data", ext = "procspec", subdir = TRUE, ignore.case = FALSE)
```

## `get_metadata()`

`get_metadata()` extracts metadata captured by the spectrophotometer during the
recording. This metadata should be reported in your scientific articles to 
ensure reproducibility of your measurements and ultimately of your findings. The
amount of information strongly depends on the brand and model of the
spectrometer.

Similarly to `get_spec()`, it can handle multiple extensions at once and perform
recursive searches:

```{r}
res <- get_metadata(where = "data", ext = c("trt", "procspec"), subdir = TRUE)
head(res)
```

## `spec2csv()`

`spec2csv()` is designed for people that want to a machine readable version for
each individual input file, possibly allowing them to carry on with their 
analysis using another programming language or software.

It works in a very similar way to `get_spec()` and will create `csv` files with
the same file names as the input files (but a different extension).

```{r}
spec2csv(where = "data", ext = "procspec", subdir = TRUE)
```
